---
title: "Day 5 Interactive Session 1"
author: "Tom Gibbens-Matsuyama"
format: html
editor: visual
execute: 
  warning: false

  
editor_options: 
  chunk_output_type: console
---

## Load Libraries

```{r}
#| message: false
# load libraries ----
library(tidyverse)
```


```{r}
#| include: false
# do some data exploration on the starwars df ----
head(starwars)
tail(starwars)
dim(starwars)
```

- Create a ggplot (scatter) of character `mass` (y-axis) and `height` (x-axis)
- update the color of th epoints so that color changes based on the value of `mass`
```{r}
#| echo: false
ggplot(data = starwars, aes(y = mass, x = height, color = mass)) +
  geom_point() +
  xlab("Height (cm)") +
  ylab("Mass(kg)")
```

- create a histogram of character heights
- update the fill color to purple and the outside border line of each histogram to orange
- update axis labels
- update code chunk options so that only your code and output graph appear in the rendered doc (no warnings or messages)

```{r}
#| message: false
#| fig-cap: "This is my figure caption"
#| fig-alt:  "This is some alt text"
ggplot(data = starwars, aes(x = height)) +
  geom_histogram(fill = "purple", color = "orange") +
  labs(x = "Height (cm)", y = "Frequency", title = "Starwars Character Heights")
```

`df$col_name`

```{r}
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE), 3)
```

The mean height of all starwars characteres is `r sw_height_mean`

